### 2015-11-30 fundamentals/impl.tex
line 339: made a slight change to the superiority claim about abm vs system dynamics. This will require a little more editing to satisfy the need to unpack the paragraph.
figure 3: makes figure 3 bigger

Furthermore, the \gls{ABM} paradigm is superior to the system dynamic approach used in
current simulators.
System dynamics is a popular approach for modeling nuclear fuel cycles
\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}.
Formally however, system dynamics models are simply a strict subset of agent-based models
\cite{macal_agent-based_2010}.
That is, any system dynamics model can be translated
into an agent-based model.
\gls{ABM} techniques therefore enable a broader range of simulations in a more
generic fashion.

@@

\gls{ABM} is inherently object-oriented because agents represent discrete,
independently acting objects.  Figure \ref{fig:framework} illustrates the
modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator creates
a set of classes on which agent plug-ins are based.  Agent plug-ins utilize the
generic core \glspl{API} that define agent-to-agent interaction as well as agent-to-environment interaction.
For example, they use the
resource exchange paradigm \gls{API} for trading resources with one another.  
For the archetype developer, these interfaces provide enormous power
very simply. The \gls{API} abstracts away unnecessary detail while providing
all necessary functionality for interacting with the \Cyclus simulation kernel.
For the user, multiple archetypes that inherit the same \glspl{API} are interchangeable
in a simulation.

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./images/agent_uml}
\end{center}
\caption{Inheriting \Cyclus class interfaces, such as the \Class{Agent},
\Class{Facility}, \Class{Institution}, and \Class{Region} classes, abstracts away
unnecessary details while exposing powerful functionality. In the above
example, the \Class{Dummy} archetype simply inherits from \Class{Region} in
order to become a bona fide Region-type \Class{Agent}.}
\label{fig:agent_uml}
\end{figure}

>>>>

Furthermore, the \gls{ABM} paradigm more flexible than the system dynamic approach used in current simulators.
System dynamics is a popular approach for modeling nuclear fuel cycles
\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}.
Formally however, system dynamics models are simply a strict subset of agent-based models
\cite{macal_agent-based_2010}.
That is, any system dynamics model can be translated
into an agent-based model.
\gls{ABM} techniques therefore enable a broader range of simulations in a more
generic fashion.

@@

\gls{ABM} is inherently object-oriented because agents represent discrete,
independently acting objects.  Figure \ref{fig:framework} illustrates the
modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator creates
a set of classes on which agent plug-ins are based.  Agent plug-ins utilize the
generic core \glspl{API} that define agent-to-agent interaction as well as agent-to-environment interaction.
For example, they use the
resource exchange paradigm \gls{API} for trading resources with one another.  
For the archetype developer, these interfaces provide enormous power
very simply. The \gls{API} abstracts away details unnecessary to specifying the 
archetype behavior, while providing
all necessary functionality for interacting with the \Cyclus simulation kernel.
For the user, multiple archetypes that inherit the same \glspl{API} are interchangeable
in a simulation.

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\textwidth]{./images/agent_uml}
\end{center}
\caption{Inheriting \Cyclus class interfaces, such as the \Class{Agent},
\Class{Facility}, \Class{Institution}, and \Class{Region} classes, abstracts away
unnecessary details while exposing powerful functionality. In the above
example, the \Class{Dummy} archetype simply inherits from \Class{Region} in
order to become a bona fide Region-type \Class{Agent}.}
\label{fig:agent_uml}
\end{figure}
